Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-05-03 docs/_tex/index.tex
adding submission files

\affiliation[1]{organization={Institut des Substances et Organismes de
la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes,
France},,postcodesep={}}
\affiliation[2]{organization={CESAM -- Centre for Environmental and
Marine Studies, Department of Biology, University of Aveiro, Aveiro,
Portugal},,postcodesep={}}
\affiliation[3]{organization={Consiglio Nazionale delle Ricerche,
Istituto di Scienze Marine (CNR-ISMAR), 00133 Rome,
Italy},,postcodesep={}}
\affiliation[4]{organization={BRGM French Geological Survey, Cayenne
97300, French Guiana},,postcodesep={}}

>>>>

\affiliation[1]{organization={Institut des Substances et Organismes de
la Mer, ISOMer, Nantes Université, UR 2160, F-44000 Nantes,
France},,postcodesep={}}
\affiliation[2]{organization={ECOMARE - Laboratory for Innovation and
Sustainability of Marine Biological Resources, CESAM -- Centre for
Environmental and Marine Studies, Department of Biology, University of
Aveiro, Campus Universitário de Santiago, 3810-193 Aveiro,
Portugal},,postcodesep={}}
\affiliation[3]{organization={Consiglio Nazionale delle Ricerche,
Istituto di Scienze Marine (CNR-ISMAR), 00133 Rome,
Italy},,postcodesep={}}
\affiliation[4]{organization={BRGM French Geological Survey, Cayenne
97300, French Guiana},,postcodesep={}}
